---
title: "Assignment03"
author: "Nabil Salehiyan"
---

Load Packages/Data

```{r}
library(haven)
library(tidyverse)
TEDS_2016 <- read_stata("https://github.com/datageneration/home/blob/master/DataProgramming/data/TEDS_2016.dta?raw=true")
```

Select only relevant variables to create a subset of the dataset (Tondu, female, DPP, age, income, edu, Taiwanese and Econ_worse). Make sure the dependent variable Tondu is coded with right labels:

```{r}
#creating a subset
subset_ <- subset(TEDS_2016, select = c("Tondu", "female", "DPP", "age", "income", "edu", "Taiwanese", "Econ_worse"))

#makes sure dependent variable is coded witht the right labels                       
TEDS_2016$Tondu<-as.numeric(TEDS_2016$Tondu,labels=c("Unification now”, “Status quo, unif. in future”, “Status quo, decide later", "Status quo forever", "Status quo, indep. in future", "Independence now”, “No response"))
```

Run a regplot on the dependent variable using age, education and, income.

```{r}
modl <- lm(Tondu ~ age + edu + income, subset_)
summary(modl)

```

```{r}
age_t <- ggplot(subset_, aes(x=age,y=Tondu)) +
  geom_smooth(method = "lm", se = F, show.legend = F, formula = y ~ x) +
  geom_point(show.legend = F, position = "jitter", alpha=.5, pch=16) +
  labs(x="Age", y="Tondu")

edu_t <- ggplot(subset_, aes(x=edu,y=Tondu)) +
  geom_smooth(method = "lm", se = F, show.legend = F, formula = y ~ x) +
  geom_point(show.legend = F, position = "jitter", alpha=.5, pch=16) +
  labs(x="Education", y="Tondu")

income_t <- ggplot(subset_, aes(x=income,y=Tondu)) +
  geom_smooth(method = "lm", se = F, show.legend = F, formula = y ~ x) +
  geom_point(show.legend = F, position = "jitter", alpha=.5, pch=16) +
  labs(x="Income", y="Tondu")

suppressWarnings(print(age_t))
```

```{r}
suppressWarnings(print(edu_t))

```

```{r}
suppressWarnings(print(income_t))
```

```{r}
unique(subset_$Tondu)

```

The problem here is that the dependent variable has 7 categories. A lin regression analysis is meant for only one dependent variable which is why the graphs look like such. A better multivariate analysis method could make more sense of this such as a **multinomial logistic regression.**

```{r}
attach(TEDS_2016)

modl <- lm(Tondu ~ female + DPP + age + income+ edu + Taiwanese + Econ_worse)

summary (modl)

subset <- subset(TEDS_2016, select = c(Tondu, female, DPP, age, income, edu, Taiwanese, Econ_worse))

library(ggplot2)

ggplot(subset, aes(x = Age, y = Tondu)) +

  geom_point() +

  geom_smooth(method = "lm")

ggplot(subset, aes(x = edu, y = Tondu)) +

  geom_point() +

  geom_smooth(method = "lm")

ggplot(subset, aes(x = income, y = Tondu)) +

  geom_point() +

  geom_smooth(method = "lm")


```
